### 2018-01-08 README.Rmd
Update README with CRAN reference

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

To install the current stable version of `infer`, make sure to install `remotes` first:

>>>>

------------------------------------------------------------------------
[![](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

To install the current stable version of `infer` from CRAN:

```{r}
install.packages("infer")
```

To install the developmental version of `infer`, make sure to install `remotes` first:
